# xtable Package Example
## Yonsei Social Science Data Analysis
### Christopher Gandrud

---

This is a short demostration of how to automatically create tables in R Markdown with the `xtable` package.

For this example, we'll first load World Bank GDP per Capita and Infant Mortality data.

```{r LoadData, warning=FALSE, message=FALSE}
# Load package
library(devtools)

# Gather data using source code at:
# http://bit.ly/OTWEGS
# Data is stored in a data frame: MortalityGDP
source_url("http://bit.ly/SFf2qz")
```

Now estimate a model with `lm`.

```{r Model, message=FALSE, warning=FALSE}
# Estimate constricted model
M1 <- lm(InfantMort ~ GDPperCapita, 
            data = MortalityGDP)
```

Finally create the table.
```{r Table, results='asis'}
# Load xtable
library(xtable)

# Create and print table
print(xtable(M1), type = "html")
```

---

**Note:** This won't work with Zelig estimated models using robust standard errors. You can get around this problem, but it takes some work. See me if you are interested.