# Automatic Tables in R Markdown
## Christopher Gandrud
## Updated 27 September 2012

---

To automatically include a table in an R Markdown document use the `xtable` package with the `print` command.

For example, let's gather some data from the internet:

```{r DataGather, message=FALSE, warning=FALSE}
# Load package
library(devtools)

# Gather data using source code at:
# http://bit.ly/OTWEGS
# Data is stored in a data frame: MortalityGDP
source_url("http://bit.ly/OTWEGS")

names(MortalityGDP)
```

Now lets summarise the variable `GDPperCapita` in the `MoralityGDP` data frame.

To do this we use the `summary` command.

```{r Sumarise}
# Sumarise MortalityGDP$GDPperCapita
Sum <- summary(MortalityGDP$GDPperCapita)

# Show contents of Sum
Sum
```

For `summaryDefault` objects we have to change them into a data frame, like this:

```{r CoerceDataFrame}
# First change to a matrix
SummaryValues <- as.matrix(Sum)

# Second change matrix to data frame
SummaryValues <- data.frame(SummaryValues)
```

Now we can use `xtable` and `print` to create an HTML table from this summary, We set the `print` argument `type = "html"` We use *knitr* to insert the table into our presentation document. To do this we need to use the *knitr* option `results='asis':

```{r CreateTable, results='asis'}
# Load xtable
library(xtable)

# Create table
print(xtable(SummaryValues), type = "html")
```
