# Using GoogleVis for Maps
## Christopher Gandrud
## Week 6: Visualisation

---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load package
library(devtools)
# Gather data using source code at:
# http://bit.ly/OTWEGS
# Data is stored in a data frame: MortalityGDP
source_url("http://bit.ly/OTWEGS")

# Create data with no missing values of infant mortali
InfantNoMiss <- subset(MortalityGDP,
                           !is.na(InfantMortality))

# Create High/Low Income Variable
InfantNoMiss$DumMort[InfantNoMiss$InfantMortality
                     >= 15] <- "high"
InfantNoMiss$DumMort[InfantNoMiss$InfantMortality
                     < 15] <- "low"
```

# Infant Mortality Map

```{r, results='asis', message=FALSE, tidy=FALSE}
# Load library
library(googleVis)

# Create infant mortality map
MortMap <- gvisGeoMap(data = MortalityGDP,
                        locationvar = "country",
                        numvar = "InfantMortality",
                      options = list(colors = "[0xEDDD00, 0xED6700, 0xA04400]")
                      )

print(MortMap, "chart")
```

### Notes

- The results probably won't show up in the RStudio Preview window. You will need to open the HTML file in your web browser.

- To include in R Markdown you need to set the chunk option `results='asis`.

- Also it is important to `print` the map and use the argument `"chart"`.

- I probably need to change the name of "Russia",